Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-07-18 Submission.Rmd
updating intro

The second set of analyses focuses on predicted associations without relevant work-relevant outcomes frequently studied across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical]. Here, we specifically explore appraisals of O\*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout. As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes. See Figure \@ref(fig:ourmodel) for proposed associations.

@@

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta]. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. Beginning with resources, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high.

@@

>Hypothesis 3a: Engagement is predicted by resources and challenges.

>Hypothesis 3b: Strain and burnout are differentially predicted by challenges and hindrances. **Take a look at significant difference between slope coefficients (b's) of, for example, challenge-->strain & hindrance-->strain**

@@

Table \@ref(tab:chal-resource-table) summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`. H3A DESCRIPTION HERE: resource slope is significant, challenge is not significant. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation. Figure \@ref(fig:chal-resource-int) illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

>>>>

The second set of predictions focuses on associations with work-relevant outcomes frequently studied across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical]. Here, we specifically explore appraisals of O\*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout. As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes. See Figure \@ref(fig:ourmodel) for proposed associations.

@@

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta]. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].

@@

>Hypothesis 3a: Resources and challenges positively predict engagement.

>Hypothesis 3b: Although both challenge and hindrance demands positively predict stress and burnout, hindrance demands are a stronger predictor of both stress and burnout.

@@

Table \@ref(tab:chal-resource-table) summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`. H3A predicted that both resources and challenges would predict engagement. Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation. Figure \@ref(fig:chal-resource-int) illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

### 2024-07-18 Submission.tex
updating intro

The second set of analyses focuses on predicted associations without relevant work-relevant outcomes frequently studied across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000). Here, we specifically explore appraisals of O*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout. As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes. See Figure \ref{fig:ourmodel} for proposed associations.

@@

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J. A. LePine et al., 2005). We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. Beginning with resources, Hakanen et al. (2008) found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high.

@@

\begin{quote}
Hypothesis 3a: Engagement is predicted by resources and challenges.
\end{quote}

\begin{quote}
Hypothesis 3b: Strain and burnout are differentially predicted by challenges and hindrances. \textbf{Take a look at significant difference between slope coefficients (b's) of, for example, challenge--\textgreater strain \& hindrance--\textgreater strain}
\end{quote}

@@

Table \ref{tab:chal-resource-table} summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj. \(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\). H3A DESCRIPTION HERE: resource slope is significant, challenge is not significant. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation. Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

@@

>>>>

The second set of predictions focuses on associations with work-relevant outcomes frequently studied across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000). Here, we specifically explore appraisals of O*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout. As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes. See Figure \ref{fig:ourmodel} for proposed associations.

@@

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J. A. LePine et al., 2005). We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, Hakanen et al. (2008) found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).

@@

\begin{quote}
Hypothesis 3a: Resources and challenges positively predict engagement.
\end{quote}

\begin{quote}
Hypothesis 3b: Although both challenge and hindrance demands positively predict stress and burnout, hindrance demands are a stronger predictor of both stress and burnout.
\end{quote}

@@

Table \ref{tab:chal-resource-table} summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj. \(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\). H3A predicted that both resources and challenges would predict engagement. Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation. Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

@@

\bibitem[\citeproctext]{ref-schaufeli2017applying}
Schaufeli, W. B. (2017). Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational Dynamics}, \emph{46}(2), 120--132.
